Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-21 07_Publication_wireframe_and_8Questions.Rmd
More writing

@@

## Why did you do it? (limit - 50 words)  
The unpublished field trial data singularly did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew. By analysing the collective data we aim to provide a better estimate for fungicide application timing to mitigate the yield loss from powdery mildew.

## what happened? (limit - 50 words)  
We found that fungicide sprays prior to when the powdery mildew was first spotted in the mungbean crop on average provided the no yield protection. A fungicide spray schedule of one or more fungicide applications commencing within three days of first sign of the disease significantly mitigated yield loss to the disease. However a fungicide spray schedule of 2 or more applications commencing four days or later than first sign of disease saved the most yield.

@@

>>>>

# Manuscript wireframe

@@

## Why did you do it? (limit - 50 words)  
The unpublished field trial data independantly did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew. By analysing the collective data we aim to provide a better estimate for fungicide application timing to mitigate the yield loss from powdery mildew.

## what happened? (limit - 50 words)  
We found that fungicide sprays prior to when the powdery mildew was first spotted in the mungbean crop on average provided no yield protection. A fungicide spray schedule of one or more fungicide applications commencing within three days of first sign of the disease significantly mitigated yield loss to the disease. However a fungicide spray schedule of 2 or more applications commencing four days or later than first sign of disease saved the most yield.

@@

# Manuscript

## Introduction  
Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia. Mungbean can potentially yield up to 2.3 tonnes per hectare, and worth up to \$ 1300 a tonne [AgMargins; 2019](https://agmargins.net.au/Reports/Details/fced3a80-a762-481c-b812-9953e33410e6). Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43%. Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.  
### Managements strategies  
#### and conditions for infection  
Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [Kelly et. al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update). In southern Queensland and northern New South Wales, planting dates between late spring (November) and mid-summer (January) are advised to avoid the conducsive cooler autumn temperatures which normally commence in March in the southern hemisphere conducive for powdery mildew establishment.  
Signs of powdery mildew are almost always first observed when temperatures start to cool.

### Fungicide resistance
Lucritive returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.

### Previous studies

### Meta-analyes

### Aims

## Materials and methods
